Check Coverage

### 2019-10-22 analysis/merge_data.Rmd
add parallelization

Get FD metrics for each study 
```{r}
load(here::here("data", "biotime_traits.rda"))

@@

fd <- map_dfr(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```

>>>>

Get FD metrics for each study 
```{r}
library(furrr)
load(here::here("data", "biotime_traits.rda"))

@@

plan(multiprocess)
fd <- future_map_dfr(combs, ~ get_fd_safe(data = data, study = .x[1], plot = .x[2]))  
```
